Red, Blue, or Grey? 2024’s Battleground States Tell a Story

### 2024-11-04 paper/paper.qmd
Paper final draft
made minor corrections on wording

```{r}
#| echo: false
#| warning: false
#| message: false
#| layout-ncol: 2
#| layout-nrow: 1
#| fig-height: 3
#| fig-width: 4

@@

# Idealized Methodology and Survey

@@

# Data Source and Preprocessing

@@

# Model details {#sec-model-details}

>>>>

```{r}
#| echo: false
#| label: fig-recency_effect
#| warning: false
#| message: false
#| layout-ncol: 2
#| layout-nrow: 1
#| fig-height: 3
#| fig-width: 4

@@

# Appendix: Idealized Methodology and Survey

@@

# Appendix: Data Source and Preprocessing

@@

# Appendix: Model details {#sec-model-details}
